Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Add other future work candidate

>>>>

We wish that our final deliverable would be either a \emph{goodness} metric, describing the quality of a ticket based 
on the information inside, or a recommender tool that could automatically create high quality tickets. This requires 
intensive work over a longer period of time, but we believe that with the findings presented in this study together 
with other state-of-the-art research in the field, it is possible to implement it.
